Worflow

### 2017-06-03 R/workflow.Rmd
put check in for current version of clusterExperiment

```{r options, echo=FALSE, results="hide",message=FALSE, error=FALSE, include=FALSE, autodep=TRUE}
knitr::opts_chunk$set(fig.align="center", cache=TRUE, error=FALSE, message=FALSE, warning=TRUE)
#bioconductor:
library(scRNAseq)
library(scone)
library(clusterExperiment)
#github
library(zinbwave)
library(slingshot)
#CRAN
library(ggplot2)
library(gplots)
library(magrittr)
library(matrixStats)
library(Rtsne)
library(RColorBrewer)
library(digest)
library(rARPACK)
set.seed(20)
```

@@

```{r examineMergeClusters}
#re-does merging simpling to make plot 
if(packageVersion("clusterExperiment")>='1.3.0.9001') mergeClusters(ceObj, mergeMethod = "locfdr", plotInfo="mergeMethod",cutoff = 0.01)
```

```{r heatmap }
if(packageVersion("clusterExperiment")>='1.3.0.9002') plotHeatmap(ceObj, clusterSamplesData="dendrogramValue", breaks = .99)
```

>>>>

```{r options, echo=FALSE, results="hide",message=FALSE, error=FALSE, include=FALSE, autodep=TRUE}
knitr::opts_chunk$set(fig.align="center", cache=TRUE, error=FALSE, message=FALSE, warning=TRUE)
#bioconductor:
library(scRNAseq)
library(scone)
library(clusterExperiment)
#github
library(zinbwave)
library(slingshot)
#CRAN
library(ggplot2)
library(gplots)
library(magrittr)
library(matrixStats)
library(Rtsne)
library(RColorBrewer)
library(digest)
library(rARPACK)
set.seed(20)
if(packageVersion("clusterExperiment")<'1.3.0.9003') stop("must have current develop version to avoid bugs")
```

@@

```{r examineMergeClusters}
#re-does merging simpling to make plot 
mergeClusters(ceObj, mergeMethod = "locfdr", plotInfo="mergeMethod",cutoff = 0.01)
```

```{r heatmap }
plotHeatmap(ceObj, clusterSamplesData="dendrogramValue", breaks = .99)
```
